Example

### 2019-04-10 example.rmd
minor change
push glmmTMB example

```{r pkgs,message=FALSE, warning=FALSE}
library(ape)
library(Matrix)
library(lme4)
library(MCMCglmm)
library(MASS) 
library(pez)
library(glmmTMB)
library(coda)
library(lattice)
library(broom)
library(dotwhisker)
```

```{r phylocode}
source("lme4_phylo_setup.R")
source("glmmTMB_phylo_setup.R")
```

@@

@@

@@

>>>>

```{r pkgs,message=FALSE, warning=FALSE}
library(ape)
library(Matrix)
library(lme4)
library(MASS) 
library(glmmTMB)
library(coda)
library(lattice)
library(broom)
library(dplyr)
```

```{r phylocode}
source("lme4_phylo_setup.R")
source("glmmTMBhacked.R")
```

@@

Similarily, fitting using glmmTMB:

```{r glmmTMB}
glmmTMB_fit <- glmmTMBhacked(phen~cofactor+(1|sp)
    , data=datG
    , phyloZ=phyloZ
    , phylonm = "sp"
    , doFit=TRUE
    , dispformula = ~1
    , REML = FALSE
  ) 
print(summary(glmmTMB_fit))
```

@@

glmmTMB_fit2 <- glmmTMBhacked(phen~spec_mean_cf+within_spec_cf+(1|sp) + (1|animals)
    , data=datR
    , phyloZ=phyloZ
    , phylonm = "sp"
    , doFit=TRUE
    , dispformula = ~1
    , REML = FALSE
  ) 
print(summary(glmmTMB_fit2))

@@

glmmTMB_fit3 <- glmmTMBhacked(phen_pois~cofactor+(1|sp)+(1|obs)
    , data=dat
    , family = poisson
    , phyloZ=phyloZ
    , phylonm = "sp"
    , doFit=TRUE
    , dispformula = ~1
    , REML = FALSE
  ) 
print(summary(glmmTMB_fit3))
